\chapter{Performance Evaluation}

\section{Methodology}

\paragraph{Datasets}
Currently there are three datasets available to run cpp\_gbdt on. Abalone, Adult and YearMSD. But it is very easy to add more: There might be a small amount of manual preprocessing necessary to get a clean input file with comma separated values from a dataset. Once this is achieved, about 15 lines of code in the Parser class are required, to specify how the new dataset looks (size, target feature, feature type, regression/classification etc.). We can only do regression and binary classification though.

\paragraph{Implementations}

\begin{itemize}
    \item python\_gbdt
\end{itemize}

\begin{itemize}
    \item cpp\_gbdt
\end{itemize}

In terms of algorithm cpp\_gbdt does exactly the same as it's python equicalent. However, there are various benefits that C/C++ gives you: Compiler optimizations, threads.

\begin{itemize}
    \item enclave\_cpp\_gbdt
\end{itemize}

This shows the effect of putting running cpp\_gbdt inside a SGX enclave. That means: no multithreading, different ways to obtain randomness. More changes TODO.

\begin{itemize}
    \item hardened\_gbdt
\end{itemize}

\section{Accuracy}

Dummy text.

\section{Runtime}

Note, all runtime results describe the amount of time spent to perform 5-fold cross validation on a dataset.
Note, many hyperparameters don't have a huge influence on runtine. But some do.


\begin{table}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|p{3.2cm}|c|c|c|c|c|c|c|c|}
      \hline
      \multirow{2}{3.2cm}{\textbf{Implementation}} & \multicolumn{3}{c|}{\textbf{abalone}} & \multicolumn{3}{c|}{\textbf{adult}} & \multicolumn{2}{c|}{\textbf{yearMSD}}\\
      % \hline
      % \textbf{Inactive Modes} & \textbf{Description}\\
      \cline{2-9}
      & \textbf{300} & \textbf{1000} & \textbf{4177} & \textbf{300} & \textbf{1000} & \textbf{5000} & \textbf{300} & \textbf{1000}\\
      %\hhline{~--}
      \hline
      python\_gbdt & 1 & 2 & 3 & 1 & 2 & 3 & 2 & 3 \\ \hline
      cpp\_gbdt & TBD & TBD & TBD & 1 & 2 & 3 & 2 & 3 \\ \hline
      enclave\_gbdt & TBD & TBD & TBD & 1 & 2 & 3 & 2 & 3 \\ \hline
      hardened\_gbdt & TBD & TBD & TBD & 1 & 2 & 3 & 2 & 3 \\ \hline
      hardened\_sgx\_gbdt & 1 & 2 & 3 & 1 & 2 & 3 & 2 & 3 \\ \hline
    \end{tabular}
    \caption{Runtime [s] 5-fold cross validation}
  \end{table}
